The core transcriptome of mammalian placentas and the divergence of expression with placental shape

### 2017-02-20 manuscript/manuscript.Rnw
discuss core placenta tree transcriptome

@@

>>>>

<<load_core_placenta_tree_transcriptome,echo=FALSE,results="hide",cache.extra=file.info("../data/placenta_core_tree_transcriptome")[,"mtime"]>>=
load("../data/placenta_core_tree_transcriptome")
cpttl <-
    core.placenta.tree.transcriptome.long[!grepl("(min|median|max|all)_expression|all_but_",
                                                 Species) & housekeeping==FALSE,]
@

@@

If we use gene trees to define the core placenta transcriptome instead
of single-copy orthologs (where the mean expression for genes in the
tree which are present must be $\text{FPKM} \ge 10$), we find
\Sexpr{cpttl[,length(unique(tree_genes))]} unique gene trees which
include nearly all of the genes present in the core placenta
transcriptome (Supplemental
\cref{fig:core_placenta_tree_transcriptome,fig:core_placenta_tree_transcriptome_housekeeping}).
